---
title: "ST542 Project: Effect of Flame Retardant Exposure on Prairie Voles
author: "Lynn Huang"
date: "February 25, 2021"
output:
  pdf_document
---
# Getting Started with NHL Records & NHL Stats APIs
There are 2 datasets from the NCSU Patisaul Lab, one for neuroanatomical endpoints, one for behavioral test endpoints. The voles used in each set are NOT the same, but they do come from the same litters (same dam/sire/DOB).

## Required Packages
```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
rm(list=ls())
library(tidyverse)
library(readxl)
library(Hmisc)
library(corrplot)
library(ggplot2)
```

## Load and Clean Data
```{r Load Data}
voles.raw <- as_tibble(read_excel("Voles.xlsx", range="A1:J248", col_names=TRUE))
neuro.raw <- as_tibble(read_excel("Neuro.xlsx", col_names=TRUE))
litters <- voles[c("ID", "Litter")]
#behav <- read_excel("Behavior.xlsx", col_names=TRUE)
```

## Explore Data: Neuro
Assign litter numbers to neuro data, then average neuro data across litters.
```{r}
# Clean Data for Correlation Matrices
neuro <- neuro.raw %>% select(ID, Sex, Dose,
                              OT.Medial.PVN, AVP.Medial.PVN,
                              OT.SON, AVP.SON,
                              TH.BNST, TH.PVN) %>% filter(Dose != "5MT") %>% na.omit()

neuro.corr <- rcorr(as.matrix(neuro[,4:9]),type = "pearson")
neuro.corr2 <- rcorr(scale(as.matrix(neuro[,4:9])),type = "pearson")
corrplot(neuro.corr$r, type="upper", p.mat=neuro.corr$P, sig.level=0.05, insig="blank")
corrplot(neuro.corr2$r, type="upper", p.mat=neuro.corr2$P, sig.level=0.05, insig="blank") # Scaling doesn't matter
# See nothing?

# Correlation Plot by Sex?
neuro.corrF <- rcorr(as.matrix(scale(filter(neuro,Sex=="F")[,4:9])),type = "pearson")
neuro.corrM <- rcorr(as.matrix(scale(filter(neuro,Sex=="M")[,4:9])),type = "pearson")
corrplot(neuro.corrF$r, type="upper", p.mat=neuro.corrF$P, sig.level=0.05, insig="blank")
corrplot(neuro.corrM$r, type="upper", p.mat=neuro.corrM$P, sig.level=0.05, insig="blank")

neuro.corrCTRL <- rcorr(as.matrix(scale(filter(neuro,Dose=="CTRL")[,4:9])),type = "pearson")
neuro.corrTRT <- rcorr(as.matrix(scale(filter(neuro,Dose!="CTRL")[,4:9])),type = "pearson")
corrplot(neuro.corrCTRL$r, type="upper", p.mat=neuro.corrCTRL$P, sig.level=0.05, insig="blank")
corrplot(neuro.corrTRT$r, type="upper", p.mat=neuro.corrTRT$P, sig.level=0.05, insig="blank")
```

```{r Old Stuff}
# Add litter numbers
neuro <- neuro %>% left_join(litters, by="ID")
# Group by sex and litter, then compute averages
neuro.litter.avg <- neuro %>% group_by(Sex, Dose) %>% summarise(Avg.OT.Medial.PVN = mean(OT.Medial.PVN),
                                                                Avg.AVP.Medial.PVN = mean(AVP.Medial.PVN),
                                                                Avg.OT.SON = mean(OT.SON),
                                                                Avg.AVP.SON = mean(AVP.SON),
                                                                Avg.TH.BNST = mean(TH.BNST),
                                                                Avg.TH.PVN = mean(TH.PVN))
# Remove NA and make Sex, Dose into factors
neuro.litter.avg <- na.omit(neuro.litter.avg)
neuro.litter.avg$Dose <- factor(neuro.litter.avg$Dose, levels=c("CTRL", "LOW", "MED", "HIGH", "5MT"))
neuro.litter.avg$Sex <- factor(neuro.litter.avg$Sex, levels=c("M", "F"))
neuro.FM550 <- neuro.litter.avg %>% filter(Dose != "5MT")

# Correlations across anything?
neuro.FM550.corr <- cor(neuro.FM550[4:9])
corrplot(neuro.FM550.corr, method="number")
# Try grouping by treatment?
neuro.5MT <- neuro.litter.avg %>% filter(Dose=="5MT")
neuro.CTRL <- neuro.litter.avg %>% filter(Dose=="CTRL")
neuro.LOW <- neuro.litter.avg %>% filter(Dose=="LOW")
neuro.MED <- neuro.litter.avg %>% filter(Dose=="MED")
neuro.HIGH <- neuro.litter.avg %>% filter(Dose=="HIGH")

# Psych
pairs.panels(neuro.litter.avg, stars = TRUE)
# Break down by dose
neuro2 <- neuro.litter.avg
neuro2$DoseAmt <- ifelse(neuro2$Dose=="CTRL", 0, 
                         ifelse(neuro2$Dose=="LOW", 500, 
                                ifelse(neuro2$Dose=="MED", 1000,
                                       ifelse(neuro2$Dose=="HIGH", 2000,
                                              ifelse(neuro2$Dose=="5MT", 0, 0)))))
pairs.panels(neuro2 %>% filter(Dose != "5MT"), stars=TRUE)



pairs(neuro.5MT[, 4:6])

# Basic numeric summaries by Dose and Sex
summary(neuro.litter.avg)

# MANOVA
neuro3 <- neuro2 %>% filter(Dose != "5MT")
fit <- manova(cbind(Avg.OT.Medial.PVN, Avg.AVP.Medial.PVN, Avg.OT.SON, Avg.AVP.SON) ~ Dose*Sex, data=neuro3)
summary(fit)
summary.aov(fit)
summary.manova(fit)

psych::outlier(neuro3[4:7])
md <- mahalanobis(neuro3[4:7], center=colMeans(neuro3[4:7]), cov = cov(neuro3[4:7]))
a <- 0.01
cutoff <- qchisq(p=1-a, df=4)
exclude <- which(md > cutoff)
neuro4 <- neuro3[-exclude,]
```